---
title: "`r params$country` Validation Report"
author: "Dalia Habiby"
date: "2023-10-27"
output: html_document
params:
  country: "Czechia"
---

```{r setup, echo = F}

suppressMessages(library(tidyverse))
suppressMessages(library(haven))
suppressMessages(library(caret))
suppressMessages(library(rio))
knitr::opts_chunk$set(echo = F)

df<- import_list(paste0("../Outcomes/Pretest/", params$country, "/", params$country, ".xlsx"))
```


```{r}
threshold<- df$tps_comparisson
time<- df$time_changes
```

```{r}
# Threshold Analysis
flags<- threshold%>%
  group_by(Pillar)%>%
  count(Flag)

problematic<- c()
notproblematic<- c()

for (p in unique(threshold$Pillar)){
  
  pillar<- flags%>%
    filter(Pillar == p)
  
  sp<- sum(pillar$n)
  
  
  if ("red" %in% unique(pillar$Flag)){
  
    if (pillar$n[pillar$Flag == "red"]/sp >0.25 | (pillar$n[pillar$Flag == "red"] + pillar$n[pillar$Flag == "yellow"])/sp > 0.5){
      
      problematic<- c(problematic, p)
    
  }
    else {
      notproblematic<- c(notproblematic, p)

  }
    
  }
  
  else if ("yellow" %in% unique(pillar$Flag)){
    
    if (pillar$n[pillar$Flag == "yellow"]/sp > 0.5){
      
      problematic<- c(problematic, p)

    }
    else {
      notproblematic<- c(notproblematic, p)

  }
  
  }
  else {
    notproblematic<- c(notproblematic, p)

  }
  
}

clevel<- c()

if (length(problematic) >= length(c(problematic, notproblematic))/2){
  clevel<-c(clevel, 1)
} else {
  
  clevel<- c(clevel,0)
}






```

```{r}
# Time change analysis

time2<- time%>%
  rename(w = warning)

time2$warning <- if_else(time2$ttestResult < 0.01, "Red light", 
                        if_else(time2$ttestResult > 0.01 & time2$ttestResult > 0.1, "Yellow light", "Green light"))

warnings<- time2%>%
  group_by(pillar)%>%
  count(warning)

problematic<- c()
notproblematic<- c()

for (p in unique(time$pillar)){
  
  pillar<- warnings%>%
    filter(pillar == p)
  
  sp<- sum(pillar$n)
  
  
  if ("Red light" %in% unique(pillar$warning)){
  
    if (pillar$n[pillar$warning == "Red light"]/sp >0.25 ){
      
      problematic<- c(problematic, p)
    
    }
    
    else if ("Yellow light" %in% unique(pillar$warning)){
      
      if ((pillar$n[pillar$warning == "Red light"] + pillar$n[pillar$warning == "Yellow light"])/sp > 0.5){
        
        problematic<- c(problematic, p)
        
      }
      else {
        notproblematic<- c(notproblematic, p)
        
      }
    }
    
  }
  
  else if ("Yellow light" %in% unique(pillar$warning)){
    
    if (pillar$n[pillar$warning == "Yellow light"]/sp > 0.5){
      
      problematic<- c(problematic, p)

    }
    else {
      notproblematic<- c(notproblematic, p)

  }
  
  }
  else {
    notproblematic<- c(notproblematic, p)

  }
  
}

if (length(problematic) >= length(c(problematic, notproblematic))/2){
  clevel<-c(clevel, 1)
} else {
  
  clevel<- c(clevel,0)
}
```



```{r}
#Country overall

if (clevel[[1]] = 1 & clevel[[2]] = 1){
  
  probl<- "problematic"
  rec<- "we recommend that the survey company should be notified of this concern and instructed about how to remedy it."
  
} else if (clevel[[1]] = 1 & clevel[[2]] = 0) {
  probl<- "problematic only in the threshold analysis"
  rec<- "we recommend that the EU GPP team should decide whether to present any concern to the survey company."
} else if (clevel[[1]] = 0 & clevel[[2]] = 1){
  probl<- "problematic only in the time change analysis"
  rec<- "we recommend that the survey company should be notified of this concern and instructed about how to remedy it."
  
} else if (clevel[[1]] = 0 & clevel[[2]] = 0){
  probl<- "not problematic"
  rec<- "we recommend that the survey company should be notified of this concern and instructed about how to remedy it."
  
}
```


## Country Level Findings

**We have found that the data from `r params$country` is `r probl`.**

Each country is evaluated based on threshold differences between an EU GPP indicator and a matched third party source indicator for each sub-pillar, as well as t-tests between the EU GPP data and the latest Global GPP data we have for that country. We determine that there is cause for concern for a specific country's data if at lease half of the Pillars evaluated are labelled "problematic."

We define a pillar as problematic in one of three cases:
  
1. If 25% or more of the sub-pillars have a threshold difference above 0.25, 
  
2. If 50% or more of the sub-pillars have a threshold difference above 0.10, or
  
3. If 50% or more of the indicators have a statistically significant difference from our last GPP

Since the data from `r params$country` is overall `r probl`, `r rec`


```{r}
flagsoutput<- flags%>%
  pivot_wider(names_from = Flag, values_from = n)

flagsoutput[is.na(flagsoutput)] <- 0
  
flagsoutput<- flagsoutput%>%
  mutate(sum = green + red + yellow )%>%
  select(Pillar, green, yellow, red, sum)

flagsoutput$Label<- ifelse(flagsoutput$red> flagsoutput$sum/4, "Problematic", ifelse(flagsoutput$red+flagsoutput$yellow > flagsoutput$sum/2, "Problematic", ifelse(flagsoutput$yellow > flagsoutput$sum/2, "Problematic", "Not Problematic")))


colnames(flagsoutput)<- c("Pillar", "Green Flags", "Yellow Flags", "Red Flags", "Total Indicators", "Label")



```

## Pillar and Sub-Pillar Details

```{r}
knitr::kable(flagsoutput)

```


```{r, results = 'asis'}

flags2<- threshold%>%
  group_by(Sub_Pillar, Pillar)%>%
  count(Flag)%>%
  pivot_wider(names_from = Flag, values_from = n)

flags2[is.na(flags2)] <- 0

ex<- c()

for (i in unique(flags2$Pillar)){
  
  pill<- filter(flags2, Pillar == i)
  
    red<- pill%>%
      filter(red > 0)
    
    r<- ifelse(nrow(red)>2, paste0(", Sub-Pillars ", paste(red$Sub_Pillar[1:(nrow(red)-1)], sep="' '", collapse=", "), ", and ", red$Sub_Pillar[[nrow(red)]], " have "), ifelse(nrow(red) == 2, paste0(", Sub-Pillars ", red$Sub_Pillar[[1]], " and ", red$Sub_Pillar[[2]], " have "), ifelse(nrow(red) ==1, paste0(", Sub-Pillar ", red$Sub_Pillar[[1]], " has "), ifelse(nrow(red)== 0, ", no Sub-Pillars have "))))
    
    yellow<- pill%>%
      filter(yellow > 0)%>%
      filter(red == 0)
    
    y<- ifelse(nrow(yellow)>2, paste0(", Sub-Pillars ", paste(yellow$Sub_Pillar[1:(nrow(yellow)-1)], sep="' '", collapse=", "), ", and ", yellow$Sub_Pillar[[nrow(yellow)]], " have "), ifelse(nrow(yellow) == 2, paste0(", Sub-Pillars ", yellow$Sub_Pillar[[1]], " and ", yellow$Sub_Pillar[[2]], " have "), ifelse(nrow(yellow) ==1, paste0(", Sub-Pillar ", yellow$Sub_Pillar[[1]], " has "), ifelse(nrow(yellow)== 0, ", no Sub-Pillars have "))))
    
    green<- pill%>%
      filter(green > 0)%>%
      filter(red == 0)%>%
      filter(yellow == 0)
    
    g<- ifelse(nrow(green)>2, paste0(" Sub-Pillars ", paste(green$Sub_Pillar[1:(nrow(green)-1)], sep="' '", collapse=", "), ", and ", green$Sub_Pillar[[nrow(green)]], " have "), ifelse(nrow(green) == 2, paste0(" Sub-Pillars ", green$Sub_Pillar[[1]], " and ", green$Sub_Pillar[[2]], " have "), ifelse(nrow(green) ==1, paste0(" Sub-Pillar ", green$Sub_Pillar[[1]], " has "), ifelse(nrow(green)== 0, " no Sub-Pillars have "))))
    
    ex<- c(ex, paste0("In Pillar ", i, r,  "high concern", y,  "moderate concern, and", g, "little to no concern."))
    
}

 
text<- paste(ex, sep="", collapse="\n")
cat(gsub(pattern = "\n", replacement = "  \n", x = text))
```

```{r}
# notes on T-test function

#produce dataframes through runme, outside of rmd, and call them in the rmd
#maybe make an excel with the GPP TPS matches so its not in the code

# we only have 17 variables to compare in t-test
# this is a problem because it is a small number

# flag country as problematic when it is flagged in both tests
# if only one, say "we only find it problematic in the threshold test/t-test"

#missing values function: count the number of people who answered more than 10% DK/PNTS
```


