---
title: '`r params$country` Full Fieldwork Validation Report'
author: '`r params$author`, Dalia Habiby'
date: '`r params$date`'
output:
  html_document: default
params:
  country: Hungary
  author: "Dalia Habiby"
  date: '2023-11-08'

---

```{r setup, echo = F}
#add to gpp folder to make sure everyone has access
suppressWarnings(suppressMessages(library(tidyverse)))
suppressWarnings(suppressMessages(library(haven)))
suppressWarnings(suppressMessages(library(caret)))
suppressWarnings(suppressMessages(library(rio)))
suppressWarnings(suppressMessages(library(kableExtra)))
suppressWarnings(suppressMessages(library(htmltools)))
suppressWarnings(library(DT))
suppressWarnings(library(crosstalk))
suppressWarnings(library(stringr))
suppressWarnings(library(DiagrammeR))
knitr::opts_chunk$set(echo = F)

if (Sys.info()["user"] == "ctoruno") {
  path2eu <- paste0("/Users/ctoruno/OneDrive - World Justice Project/EU Subnational")
  
} else if (Sys.info()["user"] == "santiagopardo") {
  path2eu <- paste0("/Users/santiagopardo/OneDrive - World Justice Project/EU Subnational")
  
} else if (Sys.info()["user"]=="Dhabiby"){
  path2eu<- paste0("/Users/Dhabiby/World Justice Project/Research - EU Subnational")
  
} else if (Sys.info()["user"]=="apillai"){
  path2eu<- paste0("/Users/apillai/OneDrive - World Justice Project/EU Subnational")
  
} else {
  path2eu <- "PLEASE INSERT YOUR PERSONAL PATH TO THE  WJP - EU SUBNATIONAL DIRECTORY"
  
}

pretest<- import_list(paste0(path2eu, "/EU-S Data/eu-data-validation/CD-valid/Outcomes/Pretest/", 
                        params$country, 
                        "/", 
                        params$country, 
                        ".xlsx"))
df<- import_list(paste0(path2eu, "/EU-S Data/eu-data-validation/CD-valid/Outcomes/Full Fieldwork/", 
                        params$country, 
                        "/", 
                        params$country, 
                        ".xlsx"))
source("paragraph.R")
par<- paragraph(params$country, type = "full")
```


```{r}

pre_thr<- pretest$tps_comparisson%>%
  select(GPP_Variable_Name, TPS_Variable_Name, Flag)%>%
  rename("Pretest Flag" = "Flag")
pre_thr$`Pretest Flag`<- ifelse(pre_thr$`Pretest Flag` == "green", "Green", ifelse(pre_thr$`Pretest Flag` == "yellow", "Yellow", "Red"))

pre_time<- pretest$time_changes%>%
  filter(warning != "Not enough info")%>%
  select(variable, warning)%>%
  rename("Pretest Flag" = "warning")
pre_time$`Pretest Flag`<- ifelse(pre_time$`Pretest Flag` == "Green light", "Green", ifelse(pre_time$`Pretest Flag` == "Yellow light", "Yellow", "Red"))

threshold1<- suppressMessages(suppressWarnings(left_join(df$tps_comparisson, pre_thr)))%>% distinct()
time<- suppressMessages(suppressWarnings(left_join(df$time_changes%>%
  filter(warning != "Not enough info"), pre_time)))%>% distinct()

experts<- threshold1%>%
  filter(Type_Survey == "expert")%>%
  drop_na()
threshold<- threshold1%>%
  filter(Type_Survey == "population")%>%
  drop_na()
```

```{r}
# Threshold Analysis for population polls
flags<- threshold%>%
  group_by(Pillar)%>%
  count(Flag)
flagssub<- threshold%>%
  group_by(Sub_Pillar)%>%
  count(Flag)

#Threshold analysis for expert surveys
flags2<- experts%>%
  group_by(Pillar)%>%
  count(Flag)
flags2sub<- experts%>%
  group_by(Sub_Pillar)%>%
  count(Flag)

# Time change analysis
warnings<- time%>%
  group_by(pillar)%>%
  count(warning)
warningssub<- time%>%
  group_by(subpillar)%>%
  count(warning)

```


# Report {.tabset}

## Guidelines

**Overview**

The goal of this document is to facilitate the evaluation of concern for extreme issues in the survey.
  
We want to preserve the validation review process that has been implemented in the past by the GPP team, while also providing more structure and a quicker way to identify potential issues. Instead of keeping track of multiple files and documents on your device, all of the relevant information lives in one dynamic platform. 
  
Our analyses are built to only identify cases of highly significant differences from our previous data as well as third party source data. We also acknowledge that many indicators are expected to change over time, or change when asked in a different way in another survey. Furthermore, our data is limited by the number of matches that can successfully be drawn from the EU GPP questionnaire to the Global GPP or to a Third Party Source. Ultimately, given these circumstances, it will still be up to the discretion of the GPP team about what and how they would like to communicate anything that might not be justified.

For the full fieldwork, our mindset is to provide the recommendations for which comparisons need more context, and the EU GPP team may dig deeper into the question level if more information is needed.
  
**Analyses**
  
Each country is evaluated based on two analyses, internal and external, disaggregated by pillar and sub-pillar. 
  
The internal and external analyses are based on a flagging system which is explained below. This has changed slightly from the pretest flagging system by removing yellow flags and making the thresholds more strict to avoid flagging too many questions. 

The first analysis is a t-test between a subset of EU GPP indicators and their counterparts from the latest Global GPP per country. 
  
We define a pillar as "significantly different" in the t-test analysis if:

- 50% or more of the indicators have a statistically significant difference from our last GPP with a p-value below 0.01 (red flag)
  
The second is a threshold difference between a few EU GPP indicators and their matched third party source indicators for each sub-pillar.
  
We define a pillar as "significantly different" in the threshold analysis if:
  
- If 50% or more of the indicators have a threshold difference above 0.35 (red flag)

Although the analysis provides summaries at both the sub-pillar and pillar levels, the unit of analysis remains the same: the indicators. Therefore, to avoid misleading results or bias given the different sizes of sub-pillars, the number of flagged sub-pillars does not affect the number of flagged pillars. 

Furthermore, the analysis classifies pillars and sub pillars differently, where pillar summaries concern whether or not they are significantly different while sub pillar summaries concern the presence and direction of underlying trends. 
  
In both of these tests, we implemented a more qualitative labeling system to incorporate general trends and direction of difference for each sub pillar. We believe that the sub pillars represent political topic areas that are tied together, and if multiple question level comparisons follow the same pattern, this may indicate a political trend that can be validated. 

- If 75% or more of the indicators in a sub pillar are red flags (as indicated above), we identify a trend 
  - If all of the indicators share the same direction of difference, this is indicated as "Potential Negative trend" or "Potential Positive trend"
  - If these indicators do not share the same direction, this is indicated as "Potential Mixed trend"
- Otherwise, the sub pillar is indicated as "No change"

  
**Process**
  
In order to utilize this document to the fullest, we suggest navigating to the "Country Level Findings" tab to view a summary of which Sub pillars or questions are concerning. The tables in each of the sub-tabs will give you an overview of all the pillars and sub pillars. From there, if any of the Pillars are significantly different, you can investigate further in the "Appendix" tab. Under the Appendix, you can select the Pillar of interest and view the analysis results as well as contextual information for each indicator that we tested. Based on the flags in the tables, it may be necessary to proceed with qualitative research to determine if the significant changes are unexpected, and therefore troublesome. 
  
Overall, this platform is a tool to help accelerate the process of identifying possible issues that should be further investigated.

As a note, scores are re-oriented, normalized, and aggregated. The scores presented in the analyses are created by re-orienting indicators if necessary to ensure that higher numbers are better for the rule of law. Then, they are normalized to fit between 0 and 1 and finally, the individual scores are aggregated by mean.

We will offer guidelines regarding which sub-pillars require further context and research to elucidate inconsistencies identified during the quantitative data validation process. We employ a systematic analysis approach using the flagging system to achieve this. Initially, we review all sub-pillars exhibiting potential trends in both the GPP over time analysis and the TPS Public Opinion Polls.

If we determine an explanation for the trends observed in the GPP over time within the TPS Public Opinion Polls, we refrain from flagging the sub-pillars. However, in instances where we cannot find an explanation for the observed trends through the intersection of both analyses, we will flag the sub-pillars in the insights summary. A summary of this selection process is presented in the following flowchart.


```{r}
mermaid(
"
graph LR
    A{Subpillars <br>flagged} --> B{Findings in GPP over time}
    A{Subpillars <br>flagged} --> C{Findings in TPS analysis}
    B{Findings in <br> GPP over time} -- Appendix --> D(Indicators flagged <br>in both analyses)
    C{Findings in <br> TPS analysis} -- Appendix --> D(Indicators flagged <br>in both analyses)
    D(Questions flagged <br>in both analyses) --> E(Match level)
    D(Questions flagged <br>in both analyses) --> F(Time difference)
    D(Questions flagged <br>in both analyses) --> G(GPP time change)

")
```

In this context, we advice to be critical about the comparisons when you are making your notes. We will provide recommendations about which comparisons need more context, however keep in mind:

- **Match level**: The comparisons with third-party sources include a column indicating the match level between the GPP and TPS questions. Comparisons with high match level should be weighted more in the overall validation.
- **Time difference**: Many relevant third party sources are from 2020 or earlier, which can cause discrepancies in the scores simply due to change over time. Comparisons with large year gaps should be weighted less in the overall validation.
- **GPP time change**: In many cases, the latest global GPP data we have is from as early as 2017, which will likely result in many flags. Comparisons with large year gaps should be weighted less in the overall validation.


## Summary of Findings {.tabset}

```{r, results= 'asis'}
par
```

```{r}
flagsoutput<- flags%>%
  pivot_wider(names_from = Flag, values_from = n)

flagsoutput[is.na(flagsoutput)] <- 0
  
flagsoutput<- flagsoutput%>%
  mutate(sum = green + red)%>%
  mutate(perc = paste0(round(red/sum*100, digits = 1), "%"))

flagsoutput$Label<- ifelse(flagsoutput$red >= flagsoutput$sum/2, "Significantly Different", "Not Significantly Different")

flagsoutput<- flagsoutput%>%
  select(Pillar, green, red, perc, Label)

colnames(flagsoutput)<- c("Pillar", "Green Flags", "Red Flags", "Percentage Red Flags", "Label")



```

```{r}

dir<- threshold
dir$Direction<- ifelse(dir$GPP_datapoint-dir$TPS_datapoint>0, "Positive", ifelse(dir$GPP_datapoint-dir$TPS_datapoint<0, "Negative", "No Change"))

dir<- dir%>%
  group_by(Sub_Pillar, Direction, Flag)%>%
  summarise(c = n(), .groups = 'drop')

dirvec<- c()

for (p in sort(unique(threshold$Sub_Pillar))){
  
  pillar<- dir%>%
    filter(Sub_Pillar == p)
  
  r<- pillar%>%
    filter(Flag == "red")
  rs<- sum(r$c)
  
  if (nrow(pillar)==1 & pillar$Flag[[1]] == "red"){
    d<- pillar$Direction[[1]]
    dirvec<- c(dirvec, paste0("Potential ", d,  " trend"))
    
  } else if (nrow(pillar)==1 & pillar$Flag[[1]] == "green"){
        dirvec<- c(dirvec, "No change")
        
     }else if (rs/sum(pillar$c)>=.75){
            
              if (nrow(r)== 1){
                d<- pillar$direction[[1]]
                dirvec<- c(dirvec, paste0("Potential ", d,  " trend"))
                
                  } else{
                    dirvec<- c(dirvec, "Potential Mixed trends")
                  }
              
              } else {
                  dirvec<- c(dirvec, "No change")
                  }
  
}


```

```{r}
flagsoutputsub<- flagssub%>%
  pivot_wider(names_from = Flag, values_from = n)

flagsoutputsub[is.na(flagsoutputsub)] <- 0
  
flagsoutputsub<- flagsoutputsub%>%
  mutate(sum = green + red )%>%
  mutate(perc = paste0(round(red/sum*100, digits = 1), "%"))

flagsoutputsub$Label<- dirvec

flagsoutputsub<- flagsoutputsub%>%
  select(Sub_Pillar, green, red, perc, Label)

colnames(flagsoutputsub)<- c("Sub-Pillar", "Green Flags", "Red Flags", "Percentage Red Flags", "Label")



```

```{r}
flagsoutput2<- flags2%>%
  pivot_wider(names_from = Flag, values_from = n)

flagsoutput2[is.na(flagsoutput2)] <- 0
  
flagsoutput2<- flagsoutput2%>%
  mutate(sum = green + red )%>%
  mutate(perc = paste0(round(red/sum*100, digits = 1), "%"))

flagsoutput2$Label<- ifelse(flagsoutput2$red >= flagsoutput2$sum/2, "Significantly Different", "Not Significantly Different")

flagsoutput2<- flagsoutput2%>%
  select(Pillar, green, red, perc, Label)

colnames(flagsoutput2)<- c("Pillar", "Green Flags", "Red Flags", "Percentage Red Flags", "Label")

```

```{r}

dir<- experts
dir$Direction<- ifelse(dir$GPP_datapoint-dir$TPS_datapoint>0, "Positive", ifelse(dir$GPP_datapoint-dir$TPS_datapoint<0, "Negative", "No Change"))

dir<- dir%>%
  group_by(Sub_Pillar, Direction, Flag)%>%
  summarise(c = n(), .groups = 'drop')

dirvec<- c()

for (p in sort(unique(experts$Sub_Pillar))){
  
  pillar<- dir%>%
    filter(Sub_Pillar == p)
  
  r<- pillar%>%
    filter(Flag == "red")
  rs<- sum(r$c)
  
  if (nrow(pillar)==1 & pillar$Flag[[1]] == "red"){
    d<- pillar$Direction[[1]]
    dirvec<- c(dirvec, paste0("Potential ", d,  " trend"))
    
  } else if (nrow(pillar)==1 & pillar$Flag[[1]] == "green"){
        dirvec<- c(dirvec, "No change")
        
     } else if (rs/sum(pillar$c)>=.75){
            
              if (nrow(r)== 1){
                d<- pillar$direction[[1]]
                dirvec<- c(dirvec, paste0("Potential ", d,  " trend"))
                
                  } else{
                    dirvec<- c(dirvec, "Potential Mixed trends")
                  }
              
              } else {
                  dirvec<- c(dirvec, "No change")
                  }
  
}


```



```{r}
flagsoutput2sub<- flags2sub%>%
  pivot_wider(names_from = Flag, values_from = n)

flagsoutput2sub[is.na(flagsoutput2sub)] <- 0
  
flagsoutput2sub<- flagsoutput2sub%>%
  mutate(sum = green + red )%>%
  mutate(perc = paste0(round(red/sum*100, digits = 1), "%"))

flagsoutput2sub$Label<- dirvec

flagsoutput2sub<- flagsoutput2sub%>%
  select(Sub_Pillar, green, red, perc, Label)

colnames(flagsoutput2sub)<- c("Sub-Pillar", "Green Flags", "Red Flags", "Percentage Red Flags", "Label")

```



```{r}
warningsoutput<- warnings%>%
  pivot_wider(names_from = warning, values_from = n)

if (!("Red light" %in% colnames(warningsoutput))){
  
  warningsoutput$`Red light`<- rep(0, nrow(warningsoutput))
}

warningsoutput[is.na(warningsoutput)] <- 0
  
warningsoutput<- warningsoutput%>%
  mutate(sum = `Green light` + `Red light`)%>%
  mutate(perc = paste0(round(`Red light`/sum*100, digits = 1), "%"))

warningsoutput$Label<- ifelse(warningsoutput$`Red light` >= warningsoutput$sum/2, "Significantly Different", "Not Significantly Different")

warningsoutput<- warningsoutput%>%
  select(pillar, `Green light`, `Red light`, perc, Label)

colnames(warningsoutput)<- c("Pillar", "Green Flags", "Red Flags", "Percentage Red Flags", "Label")

```

```{r}
dir<- time%>%
  group_by(subpillar, warning, direction)%>%
  summarise(c = n(), .groups = 'drop')

dirvec<- c()

for (p in sort(unique(time$subpillar))){
  
  pillar<- dir%>%
    filter(subpillar == p)
  
  r<- pillar%>%
    filter(warning == "Red light")
  rs<- sum(r$c)
  
  if (nrow(pillar)==1 & pillar$warning[[1]] == "Red light"){
    d<- gsub(" .*", "", pillar$direction[[1]])
    dirvec<- c(dirvec, paste0("Potential ", d,  " trend"))
    
  } else if (nrow(pillar)==1 & pillar$warning[[1]] == "Green light"){
        dirvec<- c(dirvec, "No change")
        
     } else if (rs/sum(pillar$c)>=.75){
            
              if (nrow(r)== 1){
                d<- gsub(" .*", "", pillar$direction[[1]])
                dirvec<- c(dirvec, paste0("Potential ", d,  " trend"))
                
                  } else{
                    dirvec<- c(dirvec, "Potential Mixed trends")
                  }
              
              } else {
                  dirvec<- c(dirvec, "No change")
                  }
  
}


```


```{r}
warningssuboutput<- warningssub%>%
  pivot_wider(names_from = warning, values_from = n)

if (!("Red light" %in% colnames(warningssuboutput))){
  
  warningssuboutput$`Red light`<- rep(0, nrow(warningssuboutput))
}

warningssuboutput[is.na(warningssuboutput)] <- 0
  
warningssuboutput<- warningssuboutput%>%
  mutate(sum = `Green light` + `Red light`)%>%
  mutate(perc = paste0(round(`Red light`/sum*100, digits = 1), "%"))

warningssuboutput$Label<- dirvec

warningssuboutput<- warningssuboutput%>%
  select(subpillar, `Green light`, `Red light`, perc, Label)

colnames(warningssuboutput)<- c("Sub-Pillar", "Green Flags", "Red Flags", "Percentage Red Flags", "Label")

```


```{r}

a<- threshold%>%
  select(Sub_Pillar, `2023  EU Questionnaire`, Flag, Description, TPS_Question, Match, TPS_Source, TPS_Year, GPP_datapoint, TPS_datapoint, Difference, `Pretest Flag`,  Pillar )%>%
  arrange(Sub_Pillar)
a$Direction<- ifelse(a$GPP_datapoint-a$TPS_datapoint>0, "Positive", ifelse(a$GPP_datapoint-a$TPS_datapoint<0, "Negative", "No Change"))
a$Flag<- ifelse(a$Flag == "red", "Red", ifelse(a$Flag == "green", "Green", NA))

a<- a%>%
  select(Sub_Pillar, `2023  EU Questionnaire`, Flag, Description, TPS_Question, Match, TPS_Source, TPS_Year, GPP_datapoint, TPS_datapoint, Difference, Direction, `Pretest Flag`,  Pillar )

colnames(a)<- c("Sub Pillar", "GPP Indicator", "Flag", "GPP Question",  "TPS Question", "Match Level", "TPS Source", "TPS Year", "GPP Score", "TPS Score", "Difference", "Direction", "Pretest Flag", "Pillar")



e<- experts%>%
  select(Sub_Pillar, `2023  EU Questionnaire`, Flag, Description, TPS_Question, Match, TPS_Source, TPS_Year, GPP_datapoint, TPS_datapoint, Difference, `Pretest Flag`,  Pillar )%>%
  arrange(Sub_Pillar)
e$Direction<- ifelse(e$GPP_datapoint-e$TPS_datapoint>0, "Positive", ifelse(e$GPP_datapoint-e$TPS_datapoint<0, "Negative", "No Change"))
e$Flag<- ifelse(e$Flag == "red", "Red", ifelse(e$Flag == "green", "Green", NA))

e<- e%>%
  select(Sub_Pillar, `2023  EU Questionnaire`, Flag, Description, TPS_Question, Match, TPS_Source, TPS_Year, GPP_datapoint, TPS_datapoint, Difference, Direction, `Pretest Flag`,  Pillar )

colnames(e)<- c("Sub Pillar", "GPP Indicator", "Flag", "GPP Question",  "TPS Question", "Match Level", "TPS Source", "TPS Year", "GPP Score", "TPS Score", "Difference", "Direction", "Pretest Flag", "Pillar")


b<- time%>%
  select(subpillar, `2023  EU Questionnaire`, warning, Description, prev_year, current_score, previous_score, ttestResult,  direction,  `Pretest Flag`, pillar )%>%
  arrange(subpillar)

colnames(b)<- c("Sub Pillar", "GPP Indicator", "Flag", "GPP Question", "Comparison Year", "Current Score", "Previous Score", "P value",  "Direction", "Pretest Flag", "Pillar" )

b$Flag<- ifelse(b$Flag == "Red light", "Red", ifelse(b$Flag == "Green light", "Green", NA))


tps<- threshold1%>%
  select(Sub_Pillar, `2023  EU Questionnaire`, Flag, Description, TPS_Question, Match, TPS_Source, TPS_Year, GPP_datapoint, TPS_datapoint, Difference, Type_Survey, `Pretest Flag`, Pillar )%>%
  arrange(Sub_Pillar)
tps$Direction<- ifelse(tps$GPP_datapoint-tps$TPS_datapoint>0, "Positive", ifelse(tps$GPP_datapoint-tps$TPS_datapoint<0, "Negative", "No Change"))
tps$Flag<- ifelse(tps$Flag == "red", "Red", ifelse(tps$Flag == "green", "Green", NA))

tps<- tps%>%
  select(Sub_Pillar, `2023  EU Questionnaire`, Flag, Description, TPS_Question, Match, TPS_Source, TPS_Year, GPP_datapoint, TPS_datapoint, Difference, Type_Survey, Direction, `Pretest Flag`, Pillar )
colnames(tps)<- c("Sub Pillar", "GPP Indicator", "Flag", "GPP Question",  "TPS Question", "Match Level", "TPS Source", "TPS Year", "GPP Score", "TPS Score", "Difference", "Survey Type", "Direction", "Pretest Flag", "Pillar")

```


```{r}
spmatches <- str_extract_all(par, "[0-9]\\.[0-9]{1,2}:")
spmatches <- unlist(spmatches)
popsum <- a[grepl(paste(spmatches, collapse="|"), a$`Sub Pillar`), ]
popsum <- popsum%>%
  filter(Flag == "Red")%>%
  select(-Pillar)
ttsum  <- b[grepl(paste(spmatches, collapse="|"), b$`Sub Pillar`), ]
ttsum  <- ttsum%>%
  filter(Flag == "Red")%>%
  select(-Pillar)
expsum <- e[grepl(paste(spmatches, collapse="|"), e$`Sub Pillar`), ]
expsum <- expsum%>%
  filter(Flag == "Red")%>%
  select(-Pillar)

if (nrow(ttsum)>0){

knitr::kable(ttsum, caption = "GPP Over Time", booktabs = F, escape = F, digits=3)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(full_width = F)%>%
  row_spec(0, bold= TRUE)%>%
  row_spec(which(ttsum$Flag == "Red"), background = "#FC7661", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(ttsum$Flag == "Green"), background = "#B6F161", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(ttsum$Flag == "Yellow"), background = "#FFFD69", extra_css = "border-bottom: 1px solid;")%>%
  column_spec(c(6,7,8,9,10), bold= TRUE)%>%
  remove_column(3)
    
}

if (nrow(popsum)>0 & nrow(expsum)>0){
  
  tpssum<- bind_rows(popsum, expsum)
  
knitr::kable(tpssum, caption = "TPS Analysis", booktabs = F, escape = F, digits=3)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(full_width = F)%>%
  row_spec(0, bold= TRUE)%>%
  row_spec(which(tpssum$Flag == "Red"), background = "#FC7661", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(tpssum$Flag == "Green"), background = "#B6F161", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(tpssum$Flag == "Yellow"), background = "#FFFD69", extra_css = "border-bottom: 1px solid;")%>%
  column_spec(c(9, 10, 11, 12, 13), bold= TRUE)%>%
  remove_column(3)

} else if (nrow(popsum)>0){
    
knitr::kable(popsum, caption = "TPS Analysis", booktabs = F, escape = F, digits=3)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(full_width = F)%>%
  row_spec(0, bold= TRUE)%>%
  row_spec(which(popsum$Flag == "Red"), background = "#FC7661", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(popsum$Flag == "Green"), background = "#B6F161", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(popsum$Flag == "Yellow"), background = "#FFFD69", extra_css = "border-bottom: 1px solid;")%>%
  column_spec(c(9, 10, 11, 12, 13), bold= TRUE)%>%
  remove_column(3)
  
} else if (nrow(expsum)>0){
  
  knitr::kable(expsum, caption = "TPS Analysis", booktabs = F, escape = F, digits=3)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(full_width = F)%>%
  row_spec(0, bold= TRUE)%>%
  row_spec(which(expsum$Flag == "Red"), background = "#FC7661", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(expsum$Flag == "Green"), background = "#B6F161", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(expsum$Flag == "Yellow"), background = "#FFFD69", extra_css = "border-bottom: 1px solid;")%>%
  column_spec(c(9, 10, 11, 12, 13), bold= TRUE)%>%
  remove_column(3)
  
}
```

## Country Level Results {.tabset}

Below are three tabs summarizing each of the validation analyses to provide further details about the issues we have flagged. If you are interested in exploring which specific variables are flagged, please see the Appendix.
  
```{r}
prevyr<- as.numeric(time$prev_year[1])
yrdiff<- as.numeric(time$curr_year[1]) - as.numeric(time$prev_year[1])

if (yrdiff>3){
  chnge<- "Therefore, significant changes are expected."
  
} else if (yrdiff <=3){
  
  chnge<- "Therefore, we may not expect significant changes."
}


```


### GPP Over Time
  
Since the t-test analysis this year is comparing to the previous Global GPP, there are some indicators that are new this year and do not match with the Global indicators. Therefore, there are less indicators evaluated in this analysis than the threshold analysis. Additionally, we expect many of our indicators to change in significant ways as the world changes. Therefore, it is up to the discretion of the EU GPP team whether or not the t-test results are concerning.
  
**The previous GPP data from `r params$country` is from `r prevyr` (over `r yrdiff` years old). `r chnge`**

```{r}

knitr::kable(warningsoutput, caption = "T-Test Analysis Summary", escape = F)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(bootstrap_options = c("striped"))%>%
  column_spec(5, background = ifelse(warningsoutput$Label == "Significantly Different", "#FC7661" , "#B6F161"))%>%
  column_spec(4, bold = TRUE)

knitr::kable(warningssuboutput, escape = F)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(bootstrap_options = c("striped"))%>%
  column_spec(5, background = ifelse(warningssuboutput$Label == "No change", "#B6F161", ifelse (warningssuboutput$Label == "Potential Mixed trends", "#FFFD69", "#FC7661")))%>%
  column_spec(4, bold = TRUE)%>%
  scroll_box(height = "520px", fixed_thead = T)
```


### TPS Public Opinion Polls
Given the nature of third party sources, there are a limited number of external indicators that match with our EU GPP indicators. As of now, we do not have any matches for Pillar 6. Furthermore, all of the third party indicators may not be available for each country and thus the percentage of problematic indicators in each Pillar may vary. 



```{r}

knitr::kable(flagsoutput, caption = "Threshold Analysis Summary", escape = F)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(bootstrap_options = c("striped"))%>%
  column_spec(5, background = ifelse(flagsoutput$Label == "Significantly Different", "#FC7661" , "#B6F161"))%>%
  column_spec(4, bold = TRUE)

knitr::kable(flagsoutputsub, escape = F)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(bootstrap_options = c("striped"))%>%
  column_spec(5, background = ifelse(flagsoutputsub$Label == "No change", "#B6F161", ifelse (flagsoutputsub$Label == "Potential Mixed trends", "#FFFD69", "#FC7661")))%>%
  column_spec(4, bold = TRUE)%>%
  scroll_box(height = "500px", fixed_thead = T)

```
  
  
### TPS Expert Data
Given the nature of third party sources, there are a limited number of external indicators that match with our EU GPP indicators. As of now, we do not have any matches for Pillar 6. Furthermore, all of the third party indicators may not be available for each country and thus the percentage of problematic indicators in each Pillar may vary. 



```{r}

knitr::kable(flagsoutput2, caption = "Threshold Analysis Summary", escape = F)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(bootstrap_options = c("striped"))%>%
  column_spec(5, background = ifelse(flagsoutput2$Label == "Significantly Different", "#FC7661" , "#B6F161"))%>%
  column_spec(4, bold = TRUE)

knitr::kable(flagsoutput2sub, escape = F)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(bootstrap_options = c("striped"))%>%
  column_spec(5, background = ifelse(flagsoutput2sub$Label == "No change", "#B6F161", ifelse (flagsoutput2sub$Label == "Potential Mixed trends", "#FFFD69", "#FC7661")))%>%
  column_spec(4, bold = TRUE)%>%
  scroll_box(height = "500px", fixed_thead = T)

```


## Appendix {.tabset}

Each tab below holds the full information for each analysis for each pillar in order to facilitate the evaluation of the results. At the moment, we do not have any matches in Pillar 6, and therefore there are no analysis tables for Pillar 6. 


```{r}
ttestex<- "In the T-test, a red flag indicates statistical significance with a p-value of 0.01. A green flag indicates statistical significance only with a p-value greater than 0.01, or no statistical significance."

threshex<- "In the threshold difference, a red flag indicates a difference of 0.35 or more. DISCLAIMER: some large differences may be caused by low matches between the content of the GPP and TPS questions. Make sure to account for how similar (or dissimilar) each pair is when performing qualitative checks."
```


### Pillar 1 {.tabset}

#### GPP Over Time

`r ttestex`

```{r}
b2<- b%>%
  filter(Pillar == "1: Constraints on Government Powers")%>%
  select(-Pillar)
#b2$Flag = cell_spec(b2$Flag, color = ifelse(b2$Flag == "Green", "green", ifelse(b2$Flag == "Red", "red", "gold")))

knitr::kable(b2, caption = "Variable List and Flags", booktabs = F, escape = F, digits=3)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(full_width = F)%>%
  row_spec(0, bold= TRUE)%>%
  row_spec(which(b2$Flag == "Red"), background = "#FC7661", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(b2$Flag == "Green"), background = "#B6F161", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(b2$Flag == "Yellow"), background = "#FFFD69", extra_css = "border-bottom: 1px solid;")%>%
  column_spec(c(6,7,8,9,10), bold= TRUE)%>%
  remove_column(3)%>%
  scroll_box(width = "1000px", height = "500px", fixed_thead = T)
```


#### TPS Public Opinion Polls

`r threshex`

```{r}
a2<- a%>%
  filter(Pillar == "1: Constraints on Government Powers")%>%
  select(-Pillar)

#a2$Flag = cell_spec(a2$Flag, color = ifelse(a2$Flag == "Green", "green", ifelse(a2$Flag == "Red", "red", "gold")))


knitr::kable(a2, caption = "Variable List and Flags", booktabs = F, escape = F, digits=3)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(full_width = F)%>%
  row_spec(0, bold= TRUE)%>%
  row_spec(which(a2$Flag == "Red"), background = "#FC7661", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(a2$Flag == "Green"), background = "#B6F161", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(a2$Flag == "Yellow"), background = "#FFFD69", extra_css = "border-bottom: 1px solid;")%>%
  column_spec(c(9, 10, 11, 12, 13), bold= TRUE)%>%
  remove_column(3)%>%
  scroll_box(width = "1000px", height = "500px", fixed_thead = T)
  
```

#### TPS Expert Data

`r threshex`

```{r}
e2<- e%>%
  filter(Pillar == "1: Constraints on Government Powers")%>%
  select(-Pillar)

#e2$Flag = cell_spec(e2$Flag, color = ifelse(e2$Flag == "Green", "green", ifelse(e2$Flag == "Red", "red", "gold")))


knitr::kable(e2, caption = "Variable List and Flags", booktabs = F, escape = F, digits=3)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(full_width = F)%>%
  row_spec(0, bold= TRUE)%>%
  row_spec(which(e2$Flag == "Red"), background = "#FC7661", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(e2$Flag == "Green"), background = "#B6F161", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(e2$Flag == "Yellow"), background = "#FFFD69", extra_css = "border-bottom: 1px solid;")%>%
  column_spec(c(9, 10, 11, 12, 13), bold= TRUE)%>%
  remove_column(3)%>%
  scroll_box(width = "1000px", height = "500px", fixed_thead = T)
  
```


### Pillar 2 {.tabset}

#### GPP Over Time

`r ttestex`

```{r}
b2<- b%>%
  filter(Pillar == "2: Absence of Corruption")%>%
  select(-Pillar)
#b2$Flag = cell_spec(b2$Flag, color = ifelse(b2$Flag == "Green", "green", ifelse(b2$Flag == "Red", "red", "gold")))

knitr::kable(b2, caption = "Variable List and Flags", booktabs = F, escape = F, digits=3)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(full_width = F)%>%
  row_spec(0, bold= TRUE)%>%
  row_spec(which(b2$Flag == "Red"), background = "#FC7661", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(b2$Flag == "Green"), background = "#B6F161", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(b2$Flag == "Yellow"), background = "#FFFD69", extra_css = "border-bottom: 1px solid;")%>%
  column_spec(c(6,7,8,9,10), bold= TRUE)%>%
  remove_column(3)%>%
  scroll_box(width = "1000px", height = "500px", fixed_thead = T)
```


#### TPS Public Opinion Polls

`r threshex`

```{r}
a2<- a%>%
  filter(Pillar == "2: Absence of Corruption")%>%
  select(-Pillar)

#a2$Flag = cell_spec(a2$Flag, color = ifelse(a2$Flag == "Green", "green", ifelse(a2$Flag == "Red", "red", "gold")))


knitr::kable(a2, caption = "Variable List and Flags", booktabs = F, escape = F, digits=3)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(full_width = F)%>%
  row_spec(0, bold= TRUE)%>%
  row_spec(which(a2$Flag == "Red"), background = "#FC7661", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(a2$Flag == "Green"), background = "#B6F161", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(a2$Flag == "Yellow"), background = "#FFFD69", extra_css = "border-bottom: 1px solid;")%>%
  column_spec(c(9, 10, 11, 12, 13), bold= TRUE)%>%
  remove_column(3)%>%
  scroll_box(width = "1000px", height = "500px", fixed_thead = T)
  
```

#### TPS Expert Data

`r threshex`

```{r}
e2<- e%>%
  filter(Pillar == "2: Absence of Corruption")%>%
  select(-Pillar)

#e2$Flag = cell_spec(e2$Flag, color = ifelse(e2$Flag == "Green", "green", ifelse(e2$Flag == "Red", "red", "gold")))


knitr::kable(e2, caption = "Variable List and Flags", booktabs = F, escape = F, digits=3)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(full_width = F)%>%
  row_spec(0, bold= TRUE)%>%
  row_spec(which(e2$Flag == "Red"), background = "#FC7661", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(e2$Flag == "Green"), background = "#B6F161", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(e2$Flag == "Yellow"), background = "#FFFD69", extra_css = "border-bottom: 1px solid;")%>%
  column_spec(c(9, 10, 11, 12, 13), bold= TRUE)%>%
  remove_column(3)%>%
  scroll_box(width = "1000px", height = "500px", fixed_thead = T)
  
```

### Pillar 3 {.tabset}

#### GPP Over Time

`r ttestex`

```{r}
b2<- b%>%
  filter(Pillar == "3: Open Government")%>%
  select(-Pillar)
#b2$Flag = cell_spec(b2$Flag, color = ifelse(b2$Flag == "Green", "green", ifelse(b2$Flag == "Red", "red", "gold")))

knitr::kable(b2, caption = "Variable List and Flags", booktabs = F, escape = F, digits=3)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(full_width = F)%>%
  row_spec(0, bold= TRUE)%>%
  row_spec(which(b2$Flag == "Red"), background = "#FC7661", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(b2$Flag == "Green"), background = "#B6F161", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(b2$Flag == "Yellow"), background = "#FFFD69", extra_css = "border-bottom: 1px solid;")%>%
  column_spec(c(6,7,8,9,10), bold= TRUE)%>%
  remove_column(3)%>%
  scroll_box(width = "1000px", height = "500px", fixed_thead = T)
```


#### TPS Public Opinion Polls

`r threshex`

```{r,}
a2<- a%>%
  filter(Pillar == "3: Open Government")%>%
  select(-Pillar)

#a2$Flag = cell_spec(a2$Flag, color = ifelse(a2$Flag == "Green", "green", ifelse(a2$Flag == "Red", "red", "gold")))


knitr::kable(a2, caption = "Variable List and Flags", booktabs = F, escape = F, digits=3)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(full_width = F)%>%
  row_spec(0, bold= TRUE)%>%
  row_spec(which(a2$Flag == "Red"), background = "#FC7661", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(a2$Flag == "Green"), background = "#B6F161", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(a2$Flag == "Yellow"), background = "#FFFD69", extra_css = "border-bottom: 1px solid;")%>%
  column_spec(c(9, 10, 11, 12, 13), bold= TRUE)%>%
  remove_column(3)%>%
  scroll_box(width = "1000px", height = "500px", fixed_thead = T)

  
```

#### TPS Expert Data

`r threshex`

```{r}
e2<- e%>%
  filter(Pillar == "3: Open Government")%>%
  select(-Pillar)

#e2$Flag = cell_spec(e2$Flag, color = ifelse(e2$Flag == "Green", "green", ifelse(e2$Flag == "Red", "red", "gold")))


knitr::kable(e2, caption = "Variable List and Flags", booktabs = F, escape = F, digits=3)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(full_width = F)%>%
  row_spec(0, bold= TRUE)%>%
  row_spec(which(e2$Flag == "Red"), background = "#FC7661", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(e2$Flag == "Green"), background = "#B6F161", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(e2$Flag == "Yellow"), background = "#FFFD69", extra_css = "border-bottom: 1px solid;")%>%
  column_spec(c(9, 10, 11, 12, 13), bold= TRUE)%>%
  remove_column(3)%>%
  scroll_box(width = "1000px", height = "500px", fixed_thead = T)
```

### Pillar 4 {.tabset}

#### GPP Over Time

`r ttestex`

```{r}
b2<- b%>%
  filter(Pillar == "4: Fundamental Rights")%>%
  select(-Pillar)
#b2$Flag = cell_spec(b2$Flag, color = ifelse(b2$Flag == "Green", "green", ifelse(b2$Flag == "Red", "red", "gold")))

knitr::kable(b2, caption = "Variable List and Flags", booktabs = F, escape = F, digits=3)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(full_width = F)%>%
  row_spec(0, bold= TRUE)%>%
  row_spec(which(b2$Flag == "Red"), background = "#FC7661", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(b2$Flag == "Green"), background = "#B6F161", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(b2$Flag == "Yellow"), background = "#FFFD69", extra_css = "border-bottom: 1px solid;")%>%
  column_spec(c(6,7,8,9,10), bold= TRUE)%>%
  remove_column(3)%>%
  scroll_box(width = "1000px", height = "500px", fixed_thead = T)
```


#### TPS Public Opinion Polls

`r threshex`

```{r}
a2<- a%>%
  filter(Pillar == "4: Fundamental Rights")%>%
  select(-Pillar)

#a2$Flag = cell_spec(a2$Flag, color = ifelse(a2$Flag == "Green", "green", ifelse(a2$Flag == "Red", "red", "gold")))


knitr::kable(a2, caption = "Variable List and Flags", booktabs = F, escape = F, digits=3)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(full_width = F)%>%
  row_spec(0, bold= TRUE)%>%
  row_spec(which(a2$Flag == "Red"), background = "#FC7661", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(a2$Flag == "Green"), background = "#B6F161", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(a2$Flag == "Yellow"), background = "#FFFD69", extra_css = "border-bottom: 1px solid;")%>%
  column_spec(c(9, 10, 11, 12, 13), bold= TRUE)%>%
  remove_column(3)%>%
  scroll_box(width = "1000px", height = "500px", fixed_thead = T)
  
```


#### TPS Expert Data

`r threshex`

```{r}
e2<- e%>%
  filter(Pillar == "4: Fundamental Rights")%>%
  select(-Pillar)

#e2$Flag = cell_spec(e2$Flag, color = ifelse(e2$Flag == "Green", "green", ifelse(e2$Flag == "Red", "red", "gold")))


knitr::kable(e2, caption = "Variable List and Flags", booktabs = F, escape = F, digits=3)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(full_width = F)%>%
  row_spec(0, bold= TRUE)%>%
  row_spec(which(e2$Flag == "Red"), background = "#FC7661", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(e2$Flag == "Green"), background = "#B6F161", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(e2$Flag == "Yellow"), background = "#FFFD69", extra_css = "border-bottom: 1px solid;")%>%
  column_spec(c(9, 10, 11, 12, 13), bold= TRUE)%>%
  remove_column(3)%>%
  scroll_box(width = "1000px", height = "500px", fixed_thead = T)
  
```

### Pillar 5 {.tabset}

#### GPP Over Time

`r ttestex`

```{r}
b2<- b%>%
  filter(Pillar == "5: Order and Security")%>%
  select(-Pillar)

#b2$Flag = cell_spec(b2$Flag, color = ifelse(b2$Flag == "Green", "green", ifelse(b2$Flag == "Red", "red", "gold")))

knitr::kable(b2, caption = "Variable List and Flags", booktabs = F, escape = F, digits=3)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(full_width = F)%>%
  row_spec(0, bold= TRUE)%>%
  row_spec(which(b2$Flag == "Red"), background = "#FC7661", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(b2$Flag == "Green"), background = "#B6F161", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(b2$Flag == "Yellow"), background = "#FFFD69", extra_css = "border-bottom: 1px solid;")%>%
  column_spec(c(6,7,8,9,10), bold= TRUE)%>%
  remove_column(3)%>%
  scroll_box(width = "1000px", height = "500px", fixed_thead = T)
```


#### TPS Public Opinion Polls

`r threshex`

```{r}
a2<- a%>%
  filter(Pillar == "5: Order and Security")%>%
  select(-Pillar)

#a2$Flag = cell_spec(a2$Flag, color = ifelse(a2$Flag == "Green", "green", ifelse(a2$Flag == "Red", "red", "gold")))

if (nrow(a2) >0){
  
  knitr::kable(a2, caption = "Variable List and Flags", booktabs = F, escape = F, digits=3)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(full_width = F)%>%
  row_spec(0, bold= TRUE)%>%
  row_spec(which(a2$Flag == "Red"), background = "#FC7661", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(a2$Flag == "Green"), background = "#B6F161", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(a2$Flag == "Yellow"), background = "#FFFD69", extra_css = "border-bottom: 1px solid;")%>%
  column_spec(c(9, 10, 11, 12, 13), bold= TRUE)%>%
  remove_column(3)%>%
  scroll_box(width = "1000px", height = "500px", fixed_thead = T)
  
} else{

knitr::kable(a2, caption = "Variable List and Flags", booktabs = F, escape = F, digits=3)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(full_width = F)%>%
  row_spec(0, bold= TRUE)%>%
  row_spec(which(a2$Flag == "Red"), background = "#FC7661", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(a2$Flag == "Green"), background = "#B6F161", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(a2$Flag == "Yellow"), background = "#FFFD69", extra_css = "border-bottom: 1px solid;")%>%
  scroll_box(width = "1000px", height = "500px", fixed_thead = T)

}
  
```


#### TPS Expert Data

`r threshex`

```{r}
e2<- e%>%
  filter(Pillar == "5: Order and Security")%>%
  select(-Pillar)

#e2$Flag = cell_spec(e2$Flag, color = ifelse(e2$Flag == "Green", "green", ifelse(e2$Flag == "Red", "red", "gold")))

if (nrow(e2)>0){
  
knitr::kable(e2, caption = "Variable List and Flags", booktabs = F, escape = F, digits=3)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(full_width = F)%>%
  row_spec(0, bold= TRUE)%>%
  row_spec(which(e2$Flag == "Red"), background = "#FC7661", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(e2$Flag == "Green"), background = "#B6F161", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(e2$Flag == "Yellow"), background = "#FFFD69", extra_css = "border-bottom: 1px solid;")%>%
  column_spec(c(9, 10, 11, 12, 13), bold= TRUE)%>%
  remove_column(3)%>%
  scroll_box(width = "1000px", height = "500px", fixed_thead = T)
  
} else {
  
  e2<- e2%>%
    select(-Flag)
  
  knitr::kable(e2, caption = "Variable List and Flags", booktabs = F, escape = F, digits=3)%>%
  kable_classic(html_font = "Arial", )%>%
  kable_styling(bootstrap_options = c("striped"), full_width = T)%>%
  row_spec(0, bold= TRUE)%>%
  scroll_box(width = "1000px", height = "500px", fixed_thead = T)
}
  
```

### Pillar 7 {.tabset}

#### GPP Over Time

`r ttestex`

```{r}
b2<- b%>%
  filter(Pillar == "7: Civil Justice")%>%
  select(-Pillar)
#b2$Flag = cell_spec(b2$Flag, color = ifelse(b2$Flag == "Green", "green", ifelse(b2$Flag == "Red", "red", "gold")))

knitr::kable(b2, caption = "Variable List and Flags", booktabs = F, escape = F, digits=3)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(full_width = F)%>%
  row_spec(0, bold= TRUE)%>%
  row_spec(which(b2$Flag == "Red"), background = "#FC7661", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(b2$Flag == "Green"), background = "#B6F161", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(b2$Flag == "Yellow"), background = "#FFFD69", extra_css = "border-bottom: 1px solid;")%>%
  column_spec(c(6,7,8,9,10), bold= TRUE)%>%
  remove_column(3)%>%
  scroll_box(width = "1000px", height = "500px", fixed_thead = T)
```


#### TPS Public Opinion Polls

`r threshex`

```{r}
a2<- a%>%
  filter(Pillar == "7: Civil Justice")%>%
  select(-Pillar)

#a2$Flag = cell_spec(a2$Flag, color = ifelse(a2$Flag == "Green", "green", ifelse(a2$Flag == "Red", "red", "gold")))


knitr::kable(a2, caption = "Variable List and Flags", booktabs = F, escape = F, digits=3)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(full_width = F)%>%
  row_spec(0, bold= TRUE)%>%
  row_spec(which(a2$Flag == "Red"), background = "#FC7661", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(a2$Flag == "Green"), background = "#B6F161", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(a2$Flag == "Yellow"), background = "#FFFD69", extra_css = "border-bottom: 1px solid;")%>%
  column_spec(c(9, 10, 11, 12, 13), bold= TRUE)%>%
  remove_column(3)%>%
  scroll_box(width = "1000px", height = "500px", fixed_thead = T)
  
```


#### TPS Expert Data

`r threshex`

```{r}
e2<- e%>%
  filter(Pillar == "7: Civil Justice")%>%
  select(-Pillar)

#e2$Flag = cell_spec(e2$Flag, color = ifelse(e2$Flag == "Green", "green", ifelse(e2$Flag == "Red", "red", "gold")))


knitr::kable(e2, caption = "Variable List and Flags", booktabs = F, escape = F, digits=3)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(full_width = F)%>%
  row_spec(0, bold= TRUE)%>%
  row_spec(which(e2$Flag == "Red"), background = "#FC7661", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(e2$Flag == "Green"), background = "#B6F161", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(e2$Flag == "Yellow"), background = "#FFFD69", extra_css = "border-bottom: 1px solid;")%>%
  column_spec(c(9, 10, 11, 12, 13), bold= TRUE)%>%
  remove_column(3)%>%
  scroll_box(width = "1000px", height = "500px", fixed_thead = T)
  
```

### Pillar 8 {.tabset}

#### GPP Over Time

`r ttestex`

```{r}
b2<- b%>%
  filter(Pillar == "8: Criminal Justice")%>%
  select(-Pillar)
#b2$Flag = cell_spec(b2$Flag, color = ifelse(b2$Flag == "Green", "green", ifelse(b2$Flag == "Red", "red", "gold")))

knitr::kable(b2, caption = "Variable List and Flags", booktabs = F, escape = F, digits=3)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(full_width = F)%>%
  row_spec(0, bold= TRUE)%>%
  row_spec(which(b2$Flag == "Red"), background = "#FC7661", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(b2$Flag == "Green"), background = "#B6F161", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(b2$Flag == "Yellow"), background = "#FFFD69", extra_css = "border-bottom: 1px solid;")%>%
  column_spec(c(6,7,8,9,10), bold= TRUE)%>%
  remove_column(3)%>%
  scroll_box(width = "1000px", height = "500px", fixed_thead = T)
```


#### TPS Public Opinion Polls

`r threshex`

```{r}
a2<- a%>%
  filter(Pillar == "8: Criminal Justice")%>%
  select(-Pillar)

#a2$Flag = cell_spec(a2$Flag, color = ifelse(a2$Flag == "Green", "green", ifelse(a2$Flag == "Red", "red", "gold")))


knitr::kable(a2, caption = "Variable List and Flags", booktabs = F, escape = F, digits=3)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(full_width = F)%>%
  row_spec(0, bold= TRUE)%>%
  row_spec(which(a2$Flag == "Red"), background = "#FC7661", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(a2$Flag == "Green"), background = "#B6F161", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(a2$Flag == "Yellow"), background = "#FFFD69", extra_css = "border-bottom: 1px solid;")%>%
  column_spec(c(9, 10, 11, 12, 13), bold= TRUE)%>%
  remove_column(3)%>%
  scroll_box(width = "1000px", height = "500px", fixed_thead = T)
  
```

#### TPS Expert Data

`r threshex`

```{r}
e2<- e%>%
  filter(Pillar == "8: Criminal Justice")%>%
  select(-Pillar)

#e2$Flag = cell_spec(e2$Flag, color = ifelse(e2$Flag == "Green", "green", ifelse(e2$Flag == "Red", "red", "gold")))


knitr::kable(e2, caption = "Variable List and Flags", booktabs = F, escape = F, digits=3)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(full_width = F)%>%
  row_spec(0, bold= TRUE)%>%
  row_spec(which(e2$Flag == "Red"), background = "#FC7661", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(e2$Flag == "Green"), background = "#B6F161", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(e2$Flag == "Yellow"), background = "#FFFD69", extra_css = "border-bottom: 1px solid;")%>%
  column_spec(c(9, 10, 11, 12, 13), bold= TRUE)%>%
  remove_column(3)%>%
  scroll_box(width = "1000px", height = "500px", fixed_thead = T)
  
```


### Overall {.tabset}

#### GPP Over Time

`r ttestex`

```{r}
b2<- b%>%
  select(Pillar, everything())

#b2$Flag = cell_spec(b2$Flag, color = ifelse(b2$Flag == "Green", "green", ifelse(b2$Flag == "Red", "red", "gold")))

knitr::kable(b2, caption = "Variable List and Flags", booktabs = F, escape = F, digits=3)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(full_width = F)%>%
  row_spec(0, bold= TRUE)%>%
  row_spec(which(b2$Flag == "Red"), background = "#FC7661", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(b2$Flag == "Green"), background = "#B6F161", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(b2$Flag == "Yellow"), background = "#FFFD69", extra_css = "border-bottom: 1px solid;")%>%
  column_spec(c(7,8,9,10,11), bold= TRUE)%>%
  remove_column(3)%>%
  scroll_box(width = "1000px", height = "500px", fixed_thead = T)
```

#### TPS Public Opinion Polls

`r threshex`

```{r}
a2<- a%>%
  select(Pillar, everything())
#a2$Flag = cell_spec(a2$Flag, color = ifelse(a2$Flag == "Green", "green", ifelse(a2$Flag == "Red", "red", "gold")))

knitr::kable(a2, caption = "Variable List and Flags", booktabs = F, escape = F, digits=3)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(full_width = F)%>%
  row_spec(0, bold= TRUE)%>%
  row_spec(which(a2$Flag == "Red"), background = "#FC7661", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(a2$Flag == "Green"), background = "#B6F161", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(a2$Flag == "Yellow"), background = "#FFFD69", extra_css = "border-bottom: 1px solid;")%>%
  column_spec(c(10, 11, 12, 13, 14), bold= TRUE)%>%
  remove_column(3)%>%
  scroll_box(width = "1000px", height = "500px", fixed_thead = T)

```


#### TPS Expert Data

`r threshex`

```{r}
e2<- e%>%
  select(Pillar, everything())
#e2$Flag = cell_spec(e2$Flag, color = ifelse(e2$Flag == "Green", "green", ifelse(e2$Flag == "Red", "red", "gold")))

knitr::kable(e2, caption = "Variable List and Flags", booktabs = F, escape = F, digits=3)%>%
  kable_classic(html_font = "Arial")%>%
  kable_styling(full_width = F)%>%
  row_spec(0, bold= TRUE)%>%
  row_spec(which(e2$Flag == "Red"), background = "#FC7661", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(e2$Flag == "Green"), background = "#B6F161", extra_css = "border-bottom: 1px solid;")%>%
  row_spec(which(e2$Flag == "Yellow"), background = "#FFFD69", extra_css = "border-bottom: 1px solid;")%>%
  column_spec(c(10, 11, 12, 13, 14), bold= TRUE)%>%
  remove_column(3)%>%
  scroll_box(width = "1000px", height = "500px", fixed_thead = T)

```

## Search


```{r}
# set up a group of SharedData objects
varslist<- unique(c(a$`GPP Indicator`, e$`GPP Indicator`, b$`GPP Indicator`))
z<- tibble("GPP Indicator" = varslist)

b2<- b%>%
  select(-Pillar)
tps2<- tps%>%
  select(-Pillar)

shared_gpp <- SharedData$new(b2, key = ~`GPP Indicator`, group = "shared_obj")
shared_tps <- SharedData$new(tps2, key = ~`GPP Indicator`, group = "shared_obj")
shared_comb <- SharedData$new(z, key = ~`GPP Indicator`, group = "shared_obj")

# send the group to the filtering selection box
filter_select(
  id = "id-selector", label = "GPP Indicator", 
  sharedData = shared_comb, group = ~`GPP Indicator`
)

datatable(shared_gpp, 
          rownames= FALSE, 
          caption = "GPP Over Time",
          options = list(ordering=F, dom = 't'))%>%
    formatRound(columns=c("Current Score", "Previous Score", "P value"), digits=3)
datatable(shared_tps, rownames= FALSE, 
          caption = "Third Party Source",
          options = list(ordering=F, dom = 't'))%>%
    formatRound(columns=c("GPP Score", "TPS Score", "Difference"), digits=3)

```


```{r echo = FALSE}

# varslist<- unique(c(a$`GPP Indicator`, e$`GPP Indicator`, b$`GPP Indicator`))
# 
# selectInput("var", label = "Variable",
#               choices = c(varslist), selected = "q10")
# 
# reactive(b2<- b%>%
#     filter(`GPP Indicator` == input$var))

# clr<- b2$Flag[[1]]
# 
# if (clr == "Red"){
#   
#   bkg<- "#FC7661"
# }
# if (clr == "Yellow"){
#   
#   bkg<- "#FFFD69"
# }
# if (clr == "Green"){
#   
#   bkg<- "#B6F161"
# }
#   
  
```
```{r echo = FALSE}


# htmlOutput("tableset") 
# 
# # server component
# output$tableset <- renderText({
#   kable(b2%>%
#     filter(`GPP Indicator` == input$var), caption = "GPP Over Time", booktabs = F, escape = F, digits=3)%>%
#   kable_classic(html_font = "Arial")%>%
#   kable_styling(full_width = F)
# })
# 
# 

# renderTable({
#   b%>%
#     filter(`GPP Indicator` == input$var)
# })

```


```{r}
# knitr::kable(appendix, caption = "Variable List and Flags")%>%
#   kable_classic(html_font = "Arial")%>%
#   kable_styling(bootstrap_options = c("striped"))
```


```{r, results = 'asis'}
# 
# flags2<- threshold%>%
#   group_by(Sub_Pillar, Pillar)%>%
#   count(Flag)%>%
#   pivot_wider(names_from = Flag, values_from = n)
# 
# flags2[is.na(flags2)] <- 0
# 
# ex<- c()
# 
# for (i in unique(flags2$Pillar)){
#   
#   pill<- filter(flags2, Pillar == i)
#   
#     red<- pill%>%
#       filter(red > 0)
#     
#     r<- ifelse(nrow(red)>2, paste0(", Sub-Pillars ", paste(red$Sub_Pillar[1:(nrow(red)-1)], sep="' '", collapse=", "), ", and ", red$Sub_Pillar[[nrow(red)]], " have "), ifelse(nrow(red) == 2, paste0(", Sub-Pillars ", red$Sub_Pillar[[1]], " and ", red$Sub_Pillar[[2]], " have "), ifelse(nrow(red) ==1, paste0(", Sub-Pillar ", red$Sub_Pillar[[1]], " has "), ifelse(nrow(red)== 0, ", no Sub-Pillars have "))))
#     
#     yellow<- pill%>%
#       filter(yellow > 0)%>%
#       filter(red == 0)
#     
#     y<- ifelse(nrow(yellow)>2, paste0(", Sub-Pillars ", paste(yellow$Sub_Pillar[1:(nrow(yellow)-1)], sep="' '", collapse=", "), ", and ", yellow$Sub_Pillar[[nrow(yellow)]], " have "), ifelse(nrow(yellow) == 2, paste0(", Sub-Pillars ", yellow$Sub_Pillar[[1]], " and ", yellow$Sub_Pillar[[2]], " have "), ifelse(nrow(yellow) ==1, paste0(", Sub-Pillar ", yellow$Sub_Pillar[[1]], " has "), ifelse(nrow(yellow)== 0, ", no Sub-Pillars have "))))
#     
#     green<- pill%>%
#       filter(green > 0)%>%
#       filter(red == 0)%>%
#       filter(yellow == 0)
#     
#     g<- ifelse(nrow(green)>2, paste0(" Sub-Pillars ", paste(green$Sub_Pillar[1:(nrow(green)-1)], sep="' '", collapse=", "), ", and ", green$Sub_Pillar[[nrow(green)]], " have "), ifelse(nrow(green) == 2, paste0(" Sub-Pillars ", green$Sub_Pillar[[1]], " and ", green$Sub_Pillar[[2]], " have "), ifelse(nrow(green) ==1, paste0(" Sub-Pillar ", green$Sub_Pillar[[1]], " has "), ifelse(nrow(green)== 0, " no Sub-Pillars have "))))
#     
#     ex<- c(ex, paste0("In Pillar ", i, r,  "high concern", y,  "moderate concern, and", g, "little to no concern."))
#     
# }
# 
#  
# text<- paste(ex, sep="", collapse="\n")
#cat(gsub(pattern = "\n", replacement = "  \n", x = text))
```

```{r}
# notes on T-test function

#produce dataframes through runme, outside of rmd, and call them in the rmd
#maybe make an excel with the GPP TPS matches so its not in the code

# we only have 17 variables to compare in t-test
# this is a problem because it is a small number

# flag country as problematic when it is flagged in both tests
# if only one, say "we only find it problematic in the threshold test/t-test"

#missing values function: count the number of people who answered more than 10% DK/PNTS
```




